### 2016-10-13 ARTICLES/RR_IJPP/article.tex
article.tex

\RRNo{7003}
%% \RTNo{0703}
%%
%% date de publication du rapport
\RRdate{October 2016}
%%
%% Cas d'une version deux
%% \RRversion{2}
%% date de publication de la version 2
%% \RRdater{November 2008}
%%
\RRauthor{H\'el\`ene Coullon\thanks[lip]{INRIA, LIP, ENS Lyon, 46 All\'e d'Italie, 69364 Lyon Cedex 07, France}\thanks{helene.coullon@inria.fr} \and Julien Bigot\thanks{Maison de la Simulation, CEA, CNRS, Univ. Paris-Sud, UVSQ, Universit\'e Paris-Saclay, 91191 Gif-sur-Yvette, France}\thanks{julien.bigot@cea.fr} \and Christian Perez\thanksref{lip}\thanks{christian.perez@inria.fr}}

@@

%
\begin{document}

>>>>

%% date de publication du rapport
\RRdate{October 2016}
%%
%% Cas d'une version deux
%% \RRversion{2}
%% date de publication de la version 2
%% \RRdater{November 2008}
%%
\RRauthor{H\'el\`ene Coullon\thanks[lip]{Univ. Lyon, Inria, CNRS, ENS de Lyon, Univ. Claude-Bernard Lyon 1, LIP}\thanks{\{helene.coullon\}\{christian.perez\}@inria.fr} \and Julien Bigot\thanks{Maison de la Simulation, CEA, CNRS, Univ. Paris-Sud, UVSQ, Univ. Paris-Saclay}\thanks{julien.bigot@cea.fr} \and Christian Perez}%\thanksref{lip}\thanks{christian.perez@inria.fr}}

@@

%
\begin{document}
\RRNo{8962}
